Individual heterogeneity in the functional topography of the medial prefrontal cortex

### 2019-03-07 Manuscript.Rmd
working on the draft comments from Joe

---
title: 'Individual heterogeneity in the functional topography of the DMN in medial prefrontal cortex '
author: "Claudio Toro-Serey, Sean Tobyne, & Joseph T. McGuire"
output:
  pdf_document: 
    keep_tex: true
  word_document: 
    reference_docx: Style_reference.docx
  html_document: default
bibliography: mPFC_paper.bib
header-includes:
    - \usepackage{setspace}\doublespacing
---

@@

# Perform pairwise comparisons of clustering outcomes on all subjects
comparePartitions <- function(Data = dmnval7mCommunities, MOI = "FiedlerBinary", Index = "VI", nSubjects = nSubj, subjNames = subjList) {
  # This function will compare the community partitions from all subjects and create a 'comparison matrix' for every pairwise combination of subjects
  # Alternatively, if a second MOI is added 
  # Inputs
  # 
  # Data: the list of summaries produced by the script
  # 
  # MOI: measure of interest (usually the binarized Fiedler vector). If a vector, compares across algorithms per subject
  # 
  # Index: VI for variation of information, RI for the adjusted rand index, Cor for a Pearson correlation

@@

    # Run every pairwise comparison with the index of interest on the measure of interest
    if (Index == "VI") {
      for (subj in seq(nSubjects)) {
        for (subj2 in seq(nSubjects)) {
          indexMatrix[subj,subj2] <- vi.dist(allVecs[, subj], allVecs[, subj2])
        }
      }
    } else if (Index == "RI") {
      for (subj in seq(nSubjects)) {
        for (subj2 in seq(nSubjects)) {
          indexMatrix[subj,subj2] <- arandi(allVecs[, subj], allVecs[, subj2], adjust = T)
        }
      }
    } else if (Index == "Cor") {
      for (subj in seq(nSubjects)) {
        for (subj2 in seq(nSubjects)) {
          indexMatrix[subj,subj2] <- cor(allVecs[, subj], allVecs[, subj2])
        }
      }
    }
  } else {
    indexMatrix <- data.frame(SubjID = as.character(subjList),
                              Index = rep(0, nSubjects))
    # Run every pairwise comparison with the index of interest on the measure of interest
    if (Index == "VI") {
      for (subj in seq(nSubjects)) {
        indexMatrix$Index[subj] <- vi.dist(Data[[subj]][, MOI_indx[1]], Data[[subj]][, MOI_indx[2]])
      }
    } else if (Index == "RI") {
      for (subj in seq(nSubjects)) {
        indexMatrix$Index[subj] <- arandi(Data[[subj]][, MOI_indx[1]], Data[[subj]][, MOI_indx[2]], adjust = T)
      }
    } else if (Index == "Cor") {
      for (subj in seq(nSubjects)) {
        indexMatrix$Index[subj] <- cor(Data[[subj]][, MOI_indx[1]], Data[[subj]][, MOI_indx[2]])
      }
    }
  }

@@

## Abstract (**will be expanded once we decide what to keep**)

  Valuation effects are consistently observed in medial prefrontal and posterior cingulate cortex (mPFC and PCC). The spatial extent of these effects is mostly indistinguishable from the default mode network (DMN) in existing meta-analyses. However, little is known about how valuation effects fit within the broader functional architecture of mPFC and PCC, or whether that architecture is consistent or idiosyncratic across individuals. Here we complement a meta-analysis with fMRI-based graph theoretic approaches to subdivide mPFC and PCC at the single-subject level. Our results suggest the functional topography of mPFC has substantial variability across individuals. This highlights the potential usefulness of estimating brain effects at the individual level in this region, and points to limitations of aggregative methods such as coordinate-based meta-analysis in determining whether valuation and DMN effects emerge from common or separable brain systems. Our approach shows promise in addressing this issue through future manipulations of valuation.

@@

  Studies of decision making have consistently associated activity in ventromedial prefrontal cortex (vmPFC) with the subjective value (SV) assigned to decision outcomes [@Bartra2013; @Clithero2014; @Hiser2018; @Kable2007; @Levy2011]. However, the distributed cortical valuation system also includes posterior cingulate (PCC) and more extended mPFC regions, which collectively show significant spatial overlap with the default mode network (DMN) along the medial wall [@Fox2005; @Laird2009; @Yeo2011]. This shared neural coverage has prompted the question of whether (and to what extent) these two systems can be dissociated.

  Previous meta-analytic work has provided important insights on the psychological phenomena attributed to mPFC subregions. Independent coordinate-based meta-analyses have found mirroring spatial coverage in mPFC for valuation [@Bartra2013] and DMN [@Laird2009]. Whole brain analyses have shown that while more ventral mPFC regions are increasingly associated with reward-related elements of decision making, vmPFC strongly coactivates with DMN regions across the literature, with no clear topographical distinction between these phenomena [@DelaVega2016]. More focused meta-analytic work aimed at disentangling DMN from subjective value has determined that these systems are inseparable within mPFC [@Acikalin2017]. These findings highlight the multifaceted embedding of psychological constructs in subregions of mPFC, and suggest that DMN and valuation might indeed be subserved by the same neural system. However, recent activation-based meta-analytic work has demonstrated considerable domain specificity in this area [@Kragel2018]. While informative, a key limitation in distinguishing constructs through this approach is that meta-analyses often rely on information derived from group-averaged data. Averaging has traditionally been beneficial in identifying tendencies in brain function and organization when faced with short scanning sessions per subject. However, it has been shown that mPFC is subject to considerable idiosyncratic cortical folding [@Zilles2013] and inter-subject functional variability [@Mueller2013a], thus making group-averaging studies difficult to interpret.

  Seeking to remedy these shortcomings, recent work has prescribed relevance to the analysis of single subjects in fMRI. Individual analyses of fMRI data have identified idiosyncratic, reliable, and valid functional organization that would otherwise be blurred in aggregative estimations [@Laumann2015; @Gordon2017; @Gratton2018a]. Furthermore, subject-specific network arrangements have been found to predict behavioral characteristics [@Kong2018]. In regards to DMN, the trend of individualized analyses has led to finer idiosyncratic subdivisions of the DMN through careful selection of seed-based functional connectivity [@Braga2017]. It is thus possible that the indisitinguishable overlap of DMN and valuation effects can be attributed to a lack of spatial resolution that is better understood at the individual level. With this in mind, an important first step in disentangling these phenomena would be to determine the degree of topological heterogeneity of the DMN present within mPFC.

  A persistent issue in analyzing mPFC in individuals is the various factors inducing signal dropout in its more ventral segments [@Logothetis]. As such, there is value in examining all possible sources of covariation that compose DMN, instead of estimating topologies one seed at a time. Connectome-based analyses of resting state functional connectivity (rsFC) have been fruitful in characterizing individualized functional topologies that match task-induced activity [@Gordon2017; @Laumann2015; @Tobyne2017]. A popular approach to analyze these connectomes is to rely on graph theoretic methods, which provide an organic avenue to understand brain network dynamics [@Bassett2018a]. From these, community detection algorithms have been successfully utilized to section brain networks into cohesive substructures [@Garcia2017]. Such communities represent clusters of network nodes that are more connected with each other than with the rest of the network [@Fortunato2016]. Among the algorithms used to estimate these communities, modularity has been widely effective in subsectioning brain networks into multiple groups [@Garcia2017]. However, in attempting to refine the DMN topology at the individual level, dividing these regions into what belongs and does not belong to DMN makes dissection through spectral partitioning (SP) a more valuable option. In short, spectral partitioning performs eigenvalue decompositon on an adjusted form of a correlation matrix (Laplacian matrix). The resulting eigenvector corresponding to the second-lowest eigenvalue (i.e. the Fiedler vector) provides values to divide the network into a positive and a negative community [@Fiedler1975; @Belkin2003]. SP has recently been used to characterize the posterior-anterior functional gradient of the insula using rsfMRI data [@Tian2018]. This method can thus capture a refined group of brain regions that more cohesively share activation patterns during rest.

@@

### *Anatomical Correspondence*

Finally, we examined whether each idiosyncrasies in functional topology corresponded to outstanding anatomical features. To do this, we correlated each subject's thresholded Fiedler vector values with their respective cortical thickness, cortical folding, and myelin density (quantified as the ratio of T1 to T2 magnitudes at every given vertex). These simple correlations are aimed to provide a coarse sense of this possible relationship, which can be studied in depth in the future.

@@

# # Permutation analysis
# # Note: this doesn't care whether a region was uni or bilaterally activated. Maybe do that.
# # Load the coordinates as studies in a list, because for the contrast the studies are permuted
# # Use table(unlist(list)) to get the counts in that case
# setwd('./DEC')
# templist <- dir()
# studyList_sv <- lapply(templist, readr::read_csv, col_names = F)
# 
# setwd('../DMN/')
# templist <- dir()
# studyList_dmn <- lapply(templist, readr::read_csv, col_names = F)
# 
# # For each permutation, reassign the study labels, maintaining the original number of studies per condition
# allStudies <- c(studyList_sv, studyList_dmn)
# nPerms <- 1000 # stored statistics are computed @ 5k, but it's computationally demanding to do that.
# nullDist <- numeric()
# 
# for (i in seq(nPerms)) {
# 
#   if(i %in% c(nPerms*0.25, nPerms*0.5, nPerms*0.75, nPerms*0.95)) {print(paste("Completed", i/nPerms, "percent of the permutation..."))}
# 
#   # Sample all the studies and divide into 2 groups
#   randPerm <- sample(allStudies)
#   tmpSV <- randPerm[seq(length(studyList_sv))]
#   tmpDMN <- randPerm[-seq(length(studyList_sv))]
# 
#   # Count the number of times each region was reported in the literature
#   # Bilateral activations still count as 1, so we might want to reconsider that
#   tmpDF <- data.frame(Parcel = gsub("_","", Yeo_labels),
#                       SV = sapply(Yeo_labels, function(roi) {length(grep(roi, tmpSV))}),
#                       DMN = sapply(Yeo_labels, function(roi) {length(grep(roi, tmpDMN))}))
# 
#   # Perform the prop test for each pair and get the max chi-squared stat
#   nullDist[i] <- max(
#                   apply(tmpDF[,2:3], 1, function(data) {
#                     prop.test(data, c(length(tmpSV), length(tmpDMN)))$statistic
#                     }
#                   ), na.rm = T)
# 
# }
# 
# # Now do the same for the actual data, to see how it compares to the null dist
# tmpDF <- data.frame(Parcel = gsub("_","", Yeo_labels),
#                     SV = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_sv))}),
#                     DMN = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_dmn))}),
#                     propSV = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_sv))}) / length(studyList_sv),
#                     propDMN = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_dmn))}) / length(studyList_dmn))
# 
# # Perform the prop test for each pair and get the max chi-squared stat + pvalue based on the computed null distribution
# tmpDF$Chi_squared <- apply(tmpDF[,2:3], 1, function(data) {
#   round(prop.test(data, c(length(studyList_sv), length(studyList_dmn)))$statistic, digits = 2)
#   })
# tmpDF$Pval <- 1 - ecdf(nullDist)(tmpDF$Chi_squared) # probability of finding a chi-squared stat at least as large as the observed under a permuted null distribution
# 
# # ROIs that survived the threshold based on Chi-squared value (>95th quantile from null distribution -> 8.43)
# significantROIs <- tmpDF %>% filter(Chi_squared >= quantile(nullDist,0.95))

@@

# Compare SNR between PCC and mPFC per subject after thresholding (this filtering is relevant here because we aren't using ARI anymore)
tempComm_PCC <- lapply(tempComm_PCC, function(data) {data %>% filter(FiedlerVec != 0)})
tempComm_PFC <- lapply(tempComm_PFC, function(data) {data %>% filter(FiedlerVec != 0)}) 
SNR_PCCvsPFC_perm <- sapply(seq_along(tempComm_PCC), function(x) {permute(tempComm_PCC[[x]]$varCoeff, tempComm_PFC[[x]]$varCoeff)$Pval})
SNR_PCCvsPFC_perm <- p.adjust(SNR_PCCvsPFC_perm, method = "BY")
SNR_PCCvsPFC_ES <- sapply(seq_along(tempComm_PCC), function(x) {cohenD(tempComm_PCC[[x]]$varCoeff, tempComm_PFC[[x]]$varCoeff)})
prcntSig <- mean(SNR_PCCvsPFC_perm < 0.05) * 100

@@

### *Structural correspondence*

``` {r Structural correspondence, fig.align="center", echo=FALSE, message = FALSE}
# Mean of correlations
meanMyelin <- mean(sapply(Summaries, function(data) {cor(data$FiedlerVec, data$Myelin)}))
meanCurv <- mean(sapply(Summaries, function(data) {cor(data$FiedlerVec, data$Curvature)}))
meanThick <- mean(sapply(Summaries, function(data) {cor(data$FiedlerVec, data$Thickness)}))

# SD 
sdMyelin <- sd(sapply(Summaries, function(data) {cor(data$FiedlerVec, data$Myelin)}))
sdCurv <- sd(sapply(Summaries, function(data) {cor(data$FiedlerVec, data$Curvature)}))
sdThick <- sd(sapply(Summaries, function(data) {cor(data$FiedlerVec, data$Thickness)}))
```

We coarsely examined whether these idiosyncratic topographical arrangements were defined by anatomical brain features. To do so, we correlated each subject's Fiedler vector with their respective structural MRI data. On average, we found that the Fiedler vector is uncorrelated with myelin density (mean *r* = `r round(meanMyelin, digits = 2)`; SD = `r round(sdMyelin, digits = 2)`), cortical folding (mean *r* = `r round(meanCurv, digits = 2)`; SD = `r round(sdCurv, digits = 2)`), and surface thickness (mean *r* = `r round(meanThick, digits = 2)`; SD = `r round(sdThick, digits = 2)`). While these findings point at an orthogonality between structure and functional organization, they resonate with previous work that found no strong matches between intersubject functional variability and cortical thickness, and low variability in sulcal depth within DMN [@Mueller2013a].

@@

``` {r Correlation vs community detection: compute, fig.align="center", echo=FALSE, message = FALSE, cache = TRUE}
## Between halves analysis for correlation and communities (mPFC only)
Foo <- "Fighters"
unthreshComm_PFC_halves_plot <- lapply(seq_along(unthreshComm_PFC_halves_plot), function(x) cbind(unthreshComm_PFC_halves_plot[[x]], Correlation_halves_plot[[x]]))
D1 <- unthreshComm_PFC_halves_plot
D2 <- lapply(unthreshComm_PFC_halves_plot, function(data) transform(data, V1 = FiedlerVec)) # the comparison function can only take 1 column name for this stuff
Data <- c(D1,D2)
subjList_halves_plot <- rep(best$SubjID, each = 2)
allHalfCombs <- comparePartitions(Data = Data, MOI = "V1", nSubjects = 40, Index = "Cor", subjNames = c(subjList_halves_plot, subjList_halves_plot))
```

@@

# Compare correlation with community approach on mPFC
Foo <- "Fighters"
tempComm <- sapply(seq(1, length(unthreshComm_PFC_halves), by = 2), function(x) cor(unthreshComm_PFC_halves[[x]]$FiedlerVec, unthreshComm_PFC_halves[[x+1]]$FiedlerVec))
tempCor <- sapply(seq(1, length(unthreshComm_PFC_halves), by = 2), function(x) cor(Correlation_halves[[x]]$V1, Correlation_halves[[x+1]]$V1))
tempBoth <- sapply(seq(1, length(unthreshComm_PFC_halves), by = 2), function(x) cor(unthreshComm_PFC_halves[[x]]$FiedlerVec, Correlation_halves[[x+1]]$V1))
prepostComp <- data.frame(Community = tempComm, Correlation = tempCor, Between = tempBoth)
prepostComp <- melt(prepostComp)
colnames(prepostComp) <- c("Approach", "Correlation")
prepostComp_permTest <- permute(tempComm, tempCor, paired = T)
prepostComp_ES <- cohenD(tempComm, tempCor)
```

>>>>

---
title: 'Individual heterogeneity in the functional topography of the medial prefrontal cortex'
author: "Claudio Toro-Serey, Sean Tobyne, & Joseph T. McGuire"
output:
  pdf_document: 
    keep_tex: true
  word_document: 
    reference_docx: Style_reference_draft.docx
  html_document: default
bibliography: mPFC_paper.bib
header-includes:
    - \usepackage{setspace}\doublespacing
---

@@

# Perform pairwise comparisons of clustering outcomes on all subjects
comparePartitions <- function(Data = dmnval7mCommunities, MOI = "FiedlerBinary", Index = "VI", nSubjects = nSubj, subjNames = subjList) {
  # This function will compare the community partitions from all subjects and create a 'comparison matrix' for every pairwise combination of subjects
  # Alternatively, if a second MOI is added 
  # Inputs
  # 
  # Data: the list of summaries produced by the script
  # 
  # MOI: measure of interest (usually the binarized Fiedler vector). If a vector, compares across algorithms per subject
  # 
  # Index: VI for variation of information, RI for the adjusted rand index, Cor for a Pearson correlation
  # ARI can yield many decimals, thus inflating the ratios. I thus round at 4 decimals.

@@

    # Run every pairwise comparison with the index of interest on the measure of interest
    if (Index == "VI") {
      for (subj in seq(nSubjects)) {
        for (subj2 in seq(nSubjects)) {
          indexMatrix[subj,subj2] <- vi.dist(allVecs[, subj], allVecs[, subj2])
        }
      }
    } else if (Index == "RI") {
      for (subj in seq(nSubjects)) {
        for (subj2 in seq(nSubjects)) {
          indexMatrix[subj,subj2] <- arandi(allVecs[, subj], allVecs[, subj2], adjust = T)
        }
      }
    } else if (Index == "Cor") {
      for (subj in seq(nSubjects)) {
        for (subj2 in seq(nSubjects)) {
          indexMatrix[subj,subj2] <- cor(allVecs[, subj], allVecs[, subj2])
        }
      }
    }

    indexMatrix <- round(indexMatrix, digits = 4)

  } else {
    indexMatrix <- data.frame(SubjID = as.character(subjList),
                              Index = rep(0, nSubjects))
    # Run every pairwise comparison with the index of interest on the measure of interest
    if (Index == "VI") {
      for (subj in seq(nSubjects)) {
        indexMatrix$Index[subj] <- vi.dist(Data[[subj]][, MOI_indx[1]], Data[[subj]][, MOI_indx[2]])
      }
    } else if (Index == "RI") {
      for (subj in seq(nSubjects)) {
        indexMatrix$Index[subj] <- arandi(Data[[subj]][, MOI_indx[1]], Data[[subj]][, MOI_indx[2]], adjust = T)
      }
    } else if (Index == "Cor") {
      for (subj in seq(nSubjects)) {
        indexMatrix$Index[subj] <- cor(Data[[subj]][, MOI_indx[1]], Data[[subj]][, MOI_indx[2]])
      }
    }

    indexMatrix$Index <- round(indexMatrix$Index, digits = 4)

@@

## Abstract

  There is extensive topographic overlap between cortical regions associated with the default-mode network (DMN) and regions that exhibit effects of subjective value during decision making. The two sets of functional effects involve common regions of medial prefrontal cortex (mPFC) and posterior cingulate cortex (PCC). At the same time, differences between the two sets of activation patterns are apparent at the aggregated meta-analytic level, and further individual-level functional subdivisions might be obscured by group averaging. Here we used cortical surface-based meta-analysis to identify a parcel in human PCC that was preferentially implicated in DMN effects. We then used resting-state fMRI data and a data-driven network analysis algorithm, spectral partitioning, to divide mPFC/PCC into distinct cortical communities in individual participants (n=100 from the Human Connectome Project). We labeled the communities "DMN" and "non-DMN" on the basis of their overlap with the meta-analytically identified PCC region. The spectral partitioning algorithm efficiently identified individual-level cortical subdivisions that were reliable over time and across test-retest days using moderate amounts of fMRI data (30 min per day). The topography of the identified subdivisions differed across individuals, and the degree of inter-individual variability was greater in mPFC than in PCC. Our results will aid future task-based fMRI studies in identifying functionally specific cortical subdivisions, and suggest it would be premature to infer that different task manipulations call upon shared cognitive processes solely because they evoke overlapping activation in mPFC at the group or meta-analytic level.

@@

  Human medial prefrontal cortex (mPFC) and posterior cingulate cortex (PCC) are jointly associated with a large set of disparate cognitive functions [@Hiser2018; @Kragel2018], including the subjective value (SV) assigned to decision outcomes [@Bartra2013; @Clithero2014; @Hiser2018; @Kable2007; @Levy2011]. Choice-related activity in these areas has shown significant spatial overlap with the default mode network (DMN) along the medial wall [@Fox2005; @Laird2009; @Yeo2011], prompting the question of whether (and to what extent) these two systems can be dissociated.

  Previous coordinate-based meta-analyses have identified topographically similar activation patterns in mPFC for valuation [@Bartra2013; @Clithero2014] and default-mode task deactivation [@Laird2009]. More focused meta-analytic work aimed at disentangling DMN from subjective value has determined that these systems are inseparable within mPFC [@Acikalin2017], even though there is clear divergence in other areas (ventral striatum in favor of SV, with DMN exclusively on sections of PCC and the temporoparietal junction). These findings highlight the multifaceted embedding of psychological constructs in subregions of mPFC, and suggest that DMN and valuation might indeed be subserved by the same neural system.

  A key limitation of group-averaging and meta-analysis is that individual-specific functionl subdivisions can be overlooked. Averaging has traditionally been beneficial in identifying tendencies in brain function and organization when faced with short scanning sessions per subject. However, it has been shown that mPFC is subject to considerable idiosyncratic cortical folding [@Zilles2013; @Mackey2014] and inter-subject functional variability [@Mueller2013a], thus making group-averaging studies difficult to interpret.

  Seeking to remedy these shortcomings, recent work has prescribed relevance to the analysis of single subjects in fMRI. Individual analyses of fMRI data have identified idiosyncratic, reliable, and valid functional organization that would otherwise be blurred in aggregative estimations [@Laumann2015; @Gordon2017; @Gratton2018a; @Tobyne2018]. Furthermore, subject-specific network arrangements have been found to predict behavioral characteristics [@Kong2018]. In regards to DMN, the trend of individualized analyses has led to finer idiosyncratic subdivisions of the DMN through careful selection of seed-based functional connectivity [@Braga2017]. It is thus possible that the indistinguishable overlap of DMN and valuation effects can be attributed to a lack of spatial resolution that is better understood at the individual level. With this in mind, an important first step in disentangling these phenomena would be to determine the degree of topological heterogeneity of the DMN present within mPFC.

  [i'm here] As such, there is value in examining all possible sources of covariation that compose DMN. Connectome-based analyses of resting state functional connectivity (rsFC) have been fruitful in characterizing individualized functional topologies that match task-induced activity [@Gordon2017; @Laumann2015; @Tobyne2017]. A popular approach to analyze these connectomes is to rely on graph theoretic methods, which provide an organic avenue to understand brain network dynamics [@Bassett2018a]. From these, community detection algorithms have been successfully utilized to section brain networks into cohesive substructures [@Garcia2017]. Such communities represent clusters of network nodes that are more connected with each other than with the rest of the network [@Fortunato2016]. Among the algorithms used to estimate these communities, modularity has been widely effective in subsectioning brain networks into multiple groups [@Garcia2017]. However, in attempting to refine the DMN topology at the individual level, dividing these regions into what belongs and does not belong to DMN makes dissection through spectral partitioning (SP) a more valuable option. In short, spectral partitioning performs eigenvalue decompositon on an adjusted form of a correlation matrix (Laplacian matrix). The resulting eigenvector corresponding to the second-lowest eigenvalue (i.e. the Fiedler vector) provides values to divide the network into a positive and a negative community [@Fiedler1975; @Belkin2003]. SP has recently been used to characterize the posterior-anterior functional gradient of the insula using rsfMRI data [@Tian2018]. This method can thus capture a refined group of brain regions that more cohesively share activation patterns during rest.

@@

@@

# Permutation analysis
# Note: this doesn't care whether a region was uni or bilaterally activated. Maybe do that.
# Load the coordinates as studies in a list, because for the contrast the studies are permuted
# Use table(unlist(list)) to get the counts in that case
setwd('./POS')
templist <- dir()
studyList_sv <- lapply(templist, readr::read_csv, col_names = F)

setwd('../DMN/')
templist <- dir()
studyList_dmn <- lapply(templist, readr::read_csv, col_names = F)

# For each permutation, reassign the study labels, maintaining the original number of studies per condition
allStudies <- c(studyList_sv, studyList_dmn)
nPerms <- 1000 # stored statistics are computed @ 5k, but it's computationally demanding to do that.
nullDist <- numeric()
# 
# for (i in seq(nPerms)) {
# 
#   if(i %in% c(nPerms*0.25, nPerms*0.5, nPerms*0.75, nPerms*0.95)) {print(paste("Completed", i/nPerms, "percent of the permutation..."))}
# 
#   # Sample all the studies and divide into 2 groups
#   randPerm <- sample(allStudies)
#   tmpSV <- randPerm[seq(length(studyList_sv))]
#   tmpDMN <- randPerm[-seq(length(studyList_sv))]
# 
#   # Count the number of times each region was reported in the literature
#   # Bilateral activations still count as 1, so we might want to reconsider that
#   tmpDF <- data.frame(Parcel = gsub("_","", Yeo_labels),
#                       SV = sapply(Yeo_labels, function(roi) {length(grep(roi, tmpSV))}),
#                       DMN = sapply(Yeo_labels, function(roi) {length(grep(roi, tmpDMN))}))
# 
#   # Perform the prop test for each pair and get the max chi-squared stat
#   nullDist[i] <- max(
#                   apply(tmpDF[,2:3], 1, function(data) {
#                     prop.test(data, c(length(tmpSV), length(tmpDMN)))$statistic
#                     }
#                   ), na.rm = T)
# 
# }
# 
# # Now do the same for the actual data, to see how it compares to the null dist
# tmpDF <- data.frame(Parcel = gsub("_","", Yeo_labels),
#                     SV = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_sv))}),
#                     DMN = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_dmn))}),
#                     propSV = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_sv))}) / length(studyList_sv),
#                     propDMN = sapply(Yeo_labels, function(roi) {length(grep(roi, studyList_dmn))}) / length(studyList_dmn))
# 
# # Perform the prop test for each pair and get the max chi-squared stat + pvalue based on the computed null distribution
# tmpDF$Chi_squared <- apply(tmpDF[,2:3], 1, function(data) {
#   round(prop.test(data, c(length(studyList_sv), length(studyList_dmn)))$statistic, digits = 2)
#   })
# tmpDF$Pval <- 1 - ecdf(nullDist)(tmpDF$Chi_squared) # probability of finding a chi-squared stat at least as large as the observed under a permuted null distribution
# 
# # ROIs that survived the threshold based on Chi-squared value (>95th quantile from null distribution -> 8.43)
# significantROIs <- tmpDF %>% filter(Chi_squared >= quantile(nullDist,0.95))

@@

# Compare SNR between PCC and mPFC per subject after thresholding (this filtering is relevant here because we aren't using ARI anymore)
tempComm_PCC <- lapply(tempComm_PCC, filter, FiedlerVec != 0)
tempComm_PFC <- lapply(tempComm_PFC, filter, FiedlerVec != 0) 
SNR_PCCvsPFC_perm <- sapply(seq_along(tempComm_PCC), function(x) {permute(tempComm_PCC[[x]]$varCoeff, tempComm_PFC[[x]]$varCoeff)$Pval})
SNR_PCCvsPFC_perm <- p.adjust(SNR_PCCvsPFC_perm, method = "BY")
SNR_PCCvsPFC_ES <- sapply(seq_along(tempComm_PCC), function(x) {cohenD(tempComm_PCC[[x]]$varCoeff, tempComm_PFC[[x]]$varCoeff)})
prcntSig <- mean(SNR_PCCvsPFC_perm < 0.05) * 100

@@

@@

``` {r Correlation vs community detection: compute, fig.align="center", echo=FALSE, message = FALSE, cache = TRUE}
## Between halves analysis for correlation and communities (mPFC only)
unthreshComm_PFC_halves_plot <- lapply(seq_along(unthreshComm_PFC_halves_plot), function(x) cbind(unthreshComm_PFC_halves_plot[[x]], Correlation_halves_plot[[x]]))
D1 <- unthreshComm_PFC_halves_plot
D2 <- lapply(unthreshComm_PFC_halves_plot, function(data) transform(data, V1 = FiedlerVec)) # the comparison function can only take 1 column name for this stuff
Data <- c(D1,D2)
subjList_halves_plot <- rep(best$SubjID, each = 2)
allHalfCombs <- comparePartitions(Data = Data, MOI = "V1", nSubjects = 40, Index = "Cor", subjNames = c(subjList_halves_plot, subjList_halves_plot))
```

@@

# Compare correlation with community approach on mPFC
tempComm <- sapply(seq(1, length(unthreshComm_PFC_halves), by = 2), function(x) cor(unthreshComm_PFC_halves[[x]]$FiedlerVec, unthreshComm_PFC_halves[[x+1]]$FiedlerVec))
tempCor <- sapply(seq(1, length(unthreshComm_PFC_halves), by = 2), function(x) cor(Correlation_halves[[x]]$V1, Correlation_halves[[x+1]]$V1))
tempBoth <- sapply(seq(1, length(unthreshComm_PFC_halves), by = 2), function(x) cor(unthreshComm_PFC_halves[[x]]$FiedlerVec, Correlation_halves[[x+1]]$V1))
prepostComp <- data.frame(Community = tempComm, Correlation = tempCor, Between = tempBoth)
prepostComp <- melt(prepostComp)
colnames(prepostComp) <- c("Approach", "Correlation")
prepostComp_permTest <- permute(tempComm, tempCor, paired = T)
prepostComp_ES <- cohenD(tempComm, tempCor)
```
